Arc Blanc: a real time ocean simulation framework

### 2025-01-10 paper.tex
Add option for inverse forward search with tex
Remove an incoherent name for caption fig 3
Fixed typo on non submerged part

\documentclass[final]{jcgt}

@@

	\subfloat[Using $\delta = 0$.]
	{
		\includegraphics[width=0.45\textwidth]{Figures/seaDispersion0SeaState5-contrast.png}
		\label{fig:dispersion0}
	}
	\hfill
	\subfloat[Using $\delta = 1$.]
	{
		\includegraphics[width=0.45\textwidth]{Figures/seaDispersion1SeaState5-contrast.png}
		\label{fig:dispersion1}
	}
	\caption{Effect of the dispersion parameter on sea state $5$ on the Beaufort scale.}
	\label{fig:dispersionEffect}
\end{figure}

@@

\begin{figure}[!h]
	\centering
	\input{Tikz/forcesComputation.tikz}
	\caption{Summary of forces calculation. Using the same notation as Section~\ref{subsec:forces} it follows:
		the sum of the buoyancy forces \textcolor{jauneC}{$F_b$} in \textcolor{jauneC}{yellow}, applied to the center of immersion $c_i$;
		the sum of water drag force \textcolor{purpleF}{$F_w$} in \textcolor{purpleF}{purple}, applied to $c_i$ too;
		the sum of the air drag forces \textcolor{redF}{$F_a$} in \textcolor{redF}{red}, applied to the center of the submerged part;
		and finally the gravity force \textcolor{greenF}{$F_g$} in \textcolor{greenF}{green}, applied to the center of gravity.
		Different velocities are displayed above the ship:
		the wind velocity \textcolor{redF}{$v_a$} in \textcolor{redF}{red};
		the water velocity \textcolor{bleuF}{$v_w$} in \textcolor{bleuF}{blue};
		and the object velocity \textcolor{noirC}{$v$} in \textcolor{noirC}{black}.}
	\label{fig:forcesComputation}
\end{figure}

>>>>

% !TEX options=-synctex=-1 %for inverse forward search 
\documentclass[final]{jcgt}

@@

	\subfloat[Using $\delta = 0$.]
	{
		\includegraphics[width=0.45\textwidth]{Figures/seaDispersion0SeaState5-contrast.png}
		\label{fig:dispersion0}
	}
	\hfill
	\subfloat[Using $\delta = 1$.]
	{
		\includegraphics[width=0.45\textwidth]{Figures/seaDispersion1SeaState5-contrast.png}
		\label{fig:dispersion1}
	}
	\caption{Effect of the parameter $\delta$ on sea state $5$ on the Beaufort scale.}
	\label{fig:dispersionEffect}
\end{figure}

@@

\begin{figure}[!h]
	\centering
	\input{Tikz/forcesComputation.tikz}
	\caption{Summary of forces calculation. Using the same notation as Section~\ref{subsec:forces} it follows:
		the sum of the buoyancy forces \textcolor{jauneC}{$F_b$} in \textcolor{jauneC}{yellow}, applied to the center of immersion $c_i$;
		the sum of water drag force \textcolor{purpleF}{$F_w$} in \textcolor{purpleF}{purple}, applied to $c_i$ too;
		the sum of the air drag forces \textcolor{redF}{$F_a$} in \textcolor{redF}{red}, applied to the center of the unsubmerged part;
		and finally the gravity force \textcolor{greenF}{$F_g$} in \textcolor{greenF}{green}, applied to the center of gravity.
		Different velocities are displayed above the ship:
		the wind velocity \textcolor{redF}{$v_a$} in \textcolor{redF}{red};
		the water velocity \textcolor{bleuF}{$v_w$} in \textcolor{bleuF}{blue};
		and the object velocity \textcolor{noirC}{$v$} in \textcolor{noirC}{black}.}
	\label{fig:forcesComputation}
\end{figure}
